\documentclass[spanish]{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage[spanish]{babel}
\usepackage{hyperref}

\name{Felipe Triana Casta\~neda}
\address{Cl. 131a #9-59 \\ Bogot\'a, Colombia}
%\address{\url{https://ftrianakast-cedar-14.herokuapp.com/}}
\address{(+57)~$\cdot$~302~$\cdot$~8454916 \\ ftrianakast@gmail.com}


\begin{document}


%----------------------------------------------------------------------------------------
% SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}

I am a software engineer with good communication and teamwork skills. I like software architecture, data science, functional programming (Scala, Haskell), distributed systems and category theory. As a software engineer, I am able to define and put in operation architectures based in multiple programming languages and frameworks. 

\end{rSection}

%----------------------------------------------------------------------------------------
% INTERESTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Interests}

\item Distributed systems.
\item Functional programming.
\item Databases.
\item Probability and statistics.
\item Category theory.
\item Data science.


\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of los Andes, Bogot\'a D.C, Colombia} \hfill {\em August 2013} \\
BSc in Computer Science \\
Thesis SkinHealth, a system for autodetection of skin diseases using the Ontology Ontoderm.

{\bf Colegio Seminario San Juan Ap\'ostol, Facatativ\'a, Colombia} \hfill {\em 2008} \\
 High School Degree

\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{eBay}{Mar 2022 - present}{MTS 1, Software Engineer}{Berlin, Germany}
\item I lead multiple projects for supporting the Rewards platform in Europe
\item I created technical guidelines around the Rewards platform
\item I helped creting multiple microservices using Scala and Java for supporting the Rewards platform


\end{rSubsection}


\begin{rSubsection}{eBay}{Nov 2018 - Mar 2022}{Senior Software Engineer}{Berlin, Germany}
\item I helped to create a system for Rewards in eBay Europe: this includes eBay Punkte, seller rewards and buyer rewards. The rewards system serves millions of users in Europe and it was created using microservices based in Scala and Java.
\item I helped supporting eBay global initiatives including: payments, shopping cart and checkout.
\item The microservices were created using the internal infrastructure of eBay.
\item I worked in the city of Berlin working together with individuals from different cultures and nationalities.
\end{rSubsection}


\begin{rSubsection}{Zalando}{May 2017 - Nov 2018}{Software Engineer}{Berlin, Germany}
\item I worked on an intrapreneur project for Zalando called Collabary that scaled up fast. This allowed me and the team to design processes, strategies and software components that scaled up fast but also pragmatically.
\item Software backend engineer using Java and NodeJS.
\item I worked using Java 8, Spring Boot and Hibernate.
\item I worked using ExpressJS and Sequelize.
\item Database modeling using Postgres and MySQL.
\item Put in operation an infrastructure based on AWS, Docker and internal microservices Zalando tooling.
\item Deal with an international team.
\end{rSubsection}


\begin{rSubsection}{Prodigious Latin America}{March 2015 - April 2017}{Senior Software Engineer}{Bogot\'a D.C, Colombia | San Francisco, US}
\item AEM developer: components, workflows and OSGi services.
\item Webservice designer and developer over Apache Sling.  
\item Backend engineer using Java language.
\item Deal with an international and big team.
\item Worked in three projects as a technical referent: Hewllett Packard, USANA, Renault-Nissan projects.
\end{rSubsection}


\begin{rSubsection}{Aentropico SAS}{May 2014 - December 2014}{CTO}{Bogot\'a D.C, Colombia | R\'io de Janeiro, Brazil}
\item Technical leader and organization representative.
\item Technical architect: solution designer and technical referent.
\item REST API designer.
\item Backend engineer using different programming languages: Scala, NodeJS and R.
\item Implementation of software tools for analyzing data using Scala, Akka, Spark.
\item Frontend developer using Javascript(AngularJS Framework), CSS3 (Stylus preprocessor), HTML5 (Jade template engine).
\item Database designer using NoSQL technology (MongoDB).
\item Infrastructure engineer responsible of application deployments (AWS, Docker and Heroku), security (OAuth 2.0) and platform scalability.
\item Requirement engineer. Responsible for defining technological requirements from business requirements.
\item Scrum master. Sprints planning and responsible of delivery dates.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Aentropico SAS}{August 2013 - May 2014}{Full Stack Developer}{Bogot\'a D.C | R\'io de Janeiro}
\item Architectural designer of a technological platform that provides predictive analytic tools (machine learning) and advanced algorithmic techniques for any kind of business.
\item REST API Designer.
\item Backend engineer using different programming languages: Scala, NodeJS, R.
\item Implementation of software tools for analyzing data using Scala, Akka, Spark.
\item Frontend developer using Javascript(AngularJS Framework), CSS3 (Stylus preprocessor), HTML5 (Jade template engine).
\item Database designer using NoSQL technology (MongoDB).
\item Infrastructure engineer responsible for application deployments (AWS, Docker and Heroku), security (OAuth 2.0) and platform scalability.
\item Requirement engineer. Responsible for define technological requirements from business requirements.
\item Scrum master. Sprints planning and responsible of delivery dates.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IBM}{August 2012 - December 2012}{Technical Analyst}{Bogot\'a D.C}
\item Application Integration Engineer responsible of requirement definition in a bank enterprise. The work was guided by a traditional software development methodology with level 5 on CMMI.
\item Integration services implementation using the platform Websphere Message Broker.
\item Implementation of Java adapters for integration of legacy applications.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{SoftOne SAS}{June 2012 - August 2012}{Freelancer Developer}{Bogot D.C}
\item Web service development over the framework JEE for the management of IVR in an assurnce enterprise.
\item Mobile development using the platform J2ME.
\item The works was guided by an agil software methodology (Scrum)
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% PERSONAL INITIATIVES
%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Initiatives}

\begin{rSubsection}{Bogot\'a Lambda}{January 2016 - April 2017}{Coorganizer}{Bogot\'a D.C}
\item Coorganizer and promoter of a meetup related with functional programming stuff.
\item Speaker in multiple meetups about functional programming concepts using Scala and Haskell.
\item Exercices designer for practicing functional programming concepts using Scala and Haskell.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technicall skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Software architecture & SOA (REST and SOAP services), DDD, MDD, design patterns \\
Computer Science & Category Theory, Regex, algorithms \\
Programming languages & Java, Scala, Javascript, Haskell\\
Libraries & ZIO, Scalaz, Vavr \\
Frameworks and platforms &  Spring Boot, JEE, NodeJS, ExpressJS \\
Frontend & AngularJS, CSS3, HTML5, Jade, Stylus, Grunt, Gulp \\
Protocols \& APIs & XML, JSON, SOAP, REST \\
Databases & MySQL, PostgreSQL, MongoDB, Redis, Neo4j \\
Tools & Maven, SBT, Gradle, Npm, Git, SVN \\
Infrastructure & Docker, AWS, Heroku \\
Commercial platforms & AEM 6.0, CQ, Websphere Message Broker \\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECT MANAGEMENT SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{Project management skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Methodologies & Scrum, Kanban. \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
% LANGUAGES
%----------------------------------------------------------------------------------------
\begin{rSection}{Languages}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
English & Proficient\%  \\
German & Intermediate\%  \\
Spanish & Native
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Acknowledgments}

{\bf Fellowship Quiero Estudiar Uniandes} \hfill {\em 2009} \\
Universidad de los Andes, Bogot\'a D.C, Colombia.
Awarded for academic excellence and best score on national proofs for accessing higher education.

{\bf Best High school academic score} \hfill {\em 2008} \\
Colegio Seminario San Juan Ap\'ostol, Colombia.

{\bf Guest Speaker Javascript Conference, Medell\'in Colombia} \hfill {\em October 2013} \\
Guest speaker in the anual conference of Javascript in Colombia.
Subject: Visualization explorer, a dance between nodeJS and D3.js


\end{rSection}


%----------------------------------------------------------------------------------------
% CURSOS
%----------------------------------------------------------------------------------------
\begin{rSection}{Courses - Conferences}

{\bf Coursera, Yale} \hfill {\em May 2021} \\
Financial Markets
An overview of the ideas, methods, and institutions that permit human society to manage risks and foster enterprise.  Emphasis on financially-savvy leadership skills. Description of practices today and analysis of prospects for the future. Introduction to risk management and behavioral finance principles to understand the real-world functioning of securities, insurance, and banking industries.  The ultimate goal of this course is using such industries effectively and towards a better society.


{\bf Coursera, Standford} \hfill {\em April 2016} \\
Machine Learning.
This course provides a broad introduction to machine learning, datamining, and statistical pattern recognition. Topics include: (i) Supervised learning (parametric/non-parametric algorithms, support vector machines, kernels, neural networks). (ii) Unsupervised learning (clustering, dimensionality reduction, recommender systems, deep learning). (iii) Best practices in machine learning (bias/variance theory; innovation process in machine learning and AI).

{\bf Coursera, \'Ecole Polytechnique F\'ed\'erale de Lausanne} \hfill {\em May 2015} \\
Principles of Reactive Programming.
Key elements for writing reactive programs in a composable way. Find out how to apply these building blocks in the construction of message-driven systems that are scalable and resilient.

{\bf Coursera, \'Ecole Polytechnique F\'ed\'erale de Lausanne} \hfill {\em September 2014} \\
Functional Programming Principles in Scala.
Introductory and advanced subjects of functional programming using Scala.

{\bf edX, Berkeley University, California} \hfill {\em September 2010} \\
Artifitial Intelligence.
Artifitial Intelligence Principles.

\end{rSection}

\end{document}