\documentclass[spanish]{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[spanish]{babel}
\usepackage{hyperref}

\name{Felipe Triana Casta\~neda} % Your name
\address{Calle 6B No-9-26 \\ Madrid, Cundinamarca, Colombia 250030} % Your address
\address{\url{http://ftrianakast.herokuapp.com/blog}}
\address{(+55)~$\cdot$~310~$\cdot$~8187426 \\ ftrianakast@gmail.com} % Your phone number and email


\begin{document}


%----------------------------------------------------------------------------------------
% SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}

Software engineer with good communication and teamwork skills. Enthusiastic for software architecture and data science. As a software engineer I am available to define and put in operation architectures based in multiple frameworks and programming languages, and as an enthusiastic data scientist i know stadistics, network analysys and machine learning techniques.

\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Universidad de los Andes, Bogot\'a D.C, Colombia} \hfill {\em Agosto 2013} \\
BSc in Computer Science \\
Thesis SkinHealth, a system for autodetection of skin diseases using the Ontology Ontoderm.

{\bf Colegio Seminario San Juan Ap\'ostol, Facatativ\'a, Colombia} \hfill {\em 2008} \\
 High School Degree

\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\begin{rSubsection}{Aentropico SAS}{Mayo 2014 - Octubre 2014}{CTO}{Bogot\'a D.C}
\item Technological leader and organization representative.
\item REST API designer.
\item Backend engineer using different programming languages: NodeJS, R and Java.
\item Frontend developer using Javascript(AngularJS Framework), CSS3 (Stylus preprocessor), HTML5 (Jade template engine).
\item Database designer using NoSQL technology (MongoDB).
\item Infrastructure engineer responsible for application deployments (AWS, Docker and Heroku), security (OAuth 2.0) and platform scalability.
\item Requirement engineer. Responsible for define technological requirements from business requirements.
\item Scrum master. Sprints planning and responsible of delivery dates.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Aentropico SAS}{Agosto 2013 - Mayo 2014}{Full Stack Developer}{Bogot\'a D.C}
\item Architectural designer of a technological platform that provides predictive analytic tools (machine learning) and advanced algorithmic techniques for any kind of business.
\item REST API Designer.
\item Backend engineer using different programming languages: NodeJS, R and Java.
\item Frontend developer using Javascript(AngularJS Framework), CSS3 (Stylus preprocessor), HTML5 (Jade template engine).
\item Database designer using NoSQL technology (MongoDB).
\item Infrastructure engineer responsible for application deployments (AWS, Docker and Heroku), security (OAuth 2.0) and platform scalability.
\item Requirement engineer. Responsible for define technological requirements from business requirements.
\item Scrum master. Sprints planning and responsible of delivery dates.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IBM}{Agosto 2012 - Diciembre 2012}{Technical Analyst}{Bogot\'a D.C}
\item Application Integration Engineer responsible of requirement definition in a bank enterprise. The work was guided by a traditional software development methodology with level 5 on CMMI.
\item Integration services implementation using the platform Websphere Message Broker.
\item Implementation of Java adapters for integration of legacy applications.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{SoftOne SAS}{Junio 2012 - Agosto 2012}{Freelancer Developer}{Bogot\'a D.C}
\item Web service development over the framework JEE for the management of IVR in an assurnce enterprise.
\item Mobile development using the platform J2ME.
\item The works was guided by an agil software methodology (Scrum)
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS SECTIONx
%----------------------------------------------------------------------------------------

\begin{rSection}{Technicall skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Software architecture & SOA (REST and SOAP services), DDD, MDD, design patterns \\
Programming languages & Java, Scala, Javascript, Haskell, Coffeescript \\
Frameworks and platforms & NodeJS, Akka, Play framework, JEE, ExpressJS \\
Frontend & AngularJS, BackboneJS, CSS3, HTML5, Jade, Stylus, Grunt, Gulp \\
Protocols \& APIs & XML, JSON, SOAP, REST \\
Databases & MySQL, PostgreSQL, MongoDB, Redis, Neo4j \\
Tools & Maven, SBT, Npm, Git, SVN
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECT MANAGEMENT SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{Project management skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Methodologies & Scrum, XP, TSP. \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
% LANGUAGES
%----------------------------------------------------------------------------------------
\begin{rSection}{Languages}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
English & 90\%  \\
Spanish & Native
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% RECONOCIMIENTOS
%----------------------------------------------------------------------------------------
\begin{rSection}{Acknowledments}

{\bf Fellowship Quiero Estudiar Uniandes} \hfill {\em 2009} \\
Universidad de los Andes, Bogot\'a D.C, Colombia.
Awarded for academic excellence

{\bf Best High school academic score} \hfill {\em 2008} \\
Colegio Seminario San Juan Ap\'ostol, Colombia.

\end{rSection}


%----------------------------------------------------------------------------------------
% CURSOS
%----------------------------------------------------------------------------------------
\begin{rSection}{Courses - Conferences}

{\bf Coursera, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Switzerland} \hfill {\em September 2014} \\
Functional Programming Principles in Scala.
Introductory and advanced subjects of functional programming using Scala.

{\bf Speaker Javascript Conference, Medell\'in Colombia} \hfill {\em October 2013} \\
Guest speaker in the anual conference of Javascript in Colombia.
Subject: Visualization explorer, a dance between nodeJS and D3.js

{\bf edX, Berkeley University, California} \hfill {\em September 2010} \\
Artifitial Intelligence.
Artifitial Intelligence Principles.

\end{rSection}



\end{document}
